---
title: "Lab 10"
author: "Allison Gracer"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(usethis)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr::beep()
This function plays sounds when your code is done running, useful when your code takes sometime to run.

Use `beep()` to give yourself an audio alert.

## write a for loop + beep

```{r, eval = FALSE}
for (i in rev(seq(1:99))) {
  print(paste(i, "bottles of beer on the wall"))
}

beep(4)
```

## praise is nice

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!")
```


## cowsay::say to have charachters say something

```{r}
say("I love tacos!", by ="poop")
```

## usethis for everything
cowsay::say(praise::praise("You are ${ADJECTIVE}!"), by = "trilobite")

R project first, then git & Github repo.

-usethis::use_git()
-usethis::use_github()



